Forecasting the United States 2024 Presidential Election

### 2024-11-04 paper/paper.qmd
added fig 6 caption

```{r plot-probabilities, echo=FALSE, fig.width=8, fig.height=6}
#| label: fig-6
#| echo: false
#| warning: false
#| message: false
# Reshape the data for plotting
swing_long <- swing_probs %>%
  pivot_longer(cols = c("Trump", "Harris"), names_to = "Candidate", values_to = "Probability")

>>>>

```{r plot-probabilities, echo=FALSE, fig.width=8, fig.height=6}
#| label: fig-6
#| fig-cap: Probability of Each Candidate Winning in the Swing States
#| echo: false
#| warning: false
#| message: false
# Reshape the data for plotting
swing_long <- swing_probs %>%
  pivot_longer(cols = c("Trump", "Harris"), names_to = "Candidate", values_to = "Probability")
